The not so widening achievement gap: an interntational comparison of the evolution of the SES achievement gap from 2000-2015

### 2017-08-23 paper/paper.Rnw
Visualized both counterfactual difference under different tracking and cumulative change

ready_data <-
  difference_data %>%
  left_join(tracking_data, by = c("country" = "cntry_name")) %>%
  left_join(central_examination) %>%
  mutate(num_tracks = factor(tracks15y),
         age_selection = ifelse(selage >= 15, 1, 0))

mod_tracking <-
  ready_data %>%
  lm(difference ~
       num_tracks +
       age_selection +
       length +
       central_examination, data = .)

new_data <-
  data_grid(ready_data,
            selage, num_tracks, central_examination, .model = mod_tracking) %>%
  filter(complete.cases(.))

new_data$pred <- predict(mod_tracking, newdata = new_data)

new_data %>%
  ggplot(aes(selage, pred, colour = num_tracks)) +
  geom_point()

new_data %>%
  ggplot(aes(num_tracks, pred, fill = as.character(num_tracks))) +
  geom_col(position = "dodge") +
  facet_wrap(~ central_examination) +
  scale_fill_fivethirtyeight()

@@

ready_data_two <-
  difference_data %>%
  left_join(tracking_data, by = c("country" = "cntry_name")) %>%
  left_join(central_examination) %>%
  mutate(num_tracks = factor(tracks15y),
         age_selection = ifelse(selage >= 15, 1, 0))

ready_data_two <-
  ready_data_two %>%
  group_by(country) %>%
  summarize(
    cum_diff = sum(difference, na.rm = TRUE),
    length = unique(length),
    num_tracks = unique(num_tracks),
    age_selection = unique(age_selection),
    central_examination = unique(central_examination),
    avg_track = unique(ztrack)
         )

mod_tracking <-
  ready_data_two %>%
  lm(cum_diff ~ age_selection, data = .)
@

>>>>

ready_data <-
  difference_data %>%
  left_join(tracking_data, by = c("country" = "cntry_name")) %>%
  left_join(central_examination) %>%
  mutate(num_tracks = factor(car::recode(tracks15y, "5 = 4")),
         age_selection = ifelse(selage >= 15, 1, 0))

library(rstanarm)

mod_tracking <- stan_glmer(
  difference ~
    num_tracks +
    age_selection + (1 | country),
  family = gaussian(),
  data = ready_data,
  prior = normal(0, 2),
  prior_intercept = normal(0, 5),
  prior_aux = cauchy(0, 1))

# mod_tracking <-
#   ready_data %>%
#   lmer(difference ~
#        num_tracks +
#        age_selection + (1 | country), data = .)

# new_data <-
#   data_grid(ready_data,
#             selage, num_tracks, central_examination, .model = mod_tracking) %>%
#   filter(complete.cases(.))

new_data <-
  ready_data %>%
  filter(!is.na(age_selection), !is.na(num_tracks)) %>%
  expand(country, age_selection, num_tracks) %>%
  filter(complete.cases(.))

predictions <- posterior_predict(mod_tracking, newdata = new_data)
sd_obs <- colSds(predictions)

new_data$pred <- colMeans(predictions)
new_data$pred_low <- new_data$pred - (2 * sd_obs)
new_data$pred_high <- new_data$pred + (2 * sd_obs)

sum_ready_data <-
  ready_data %>%
  group_by(country, num_tracks, age_selection) %>%
  summarize(avg_diff = mean(difference),
            diff_low = avg_diff - 2 * sd(difference),
            diff_high = avg_diff + 2 * sd(difference)) %>%
  ungroup()

new_data %>% left_join(sum_ready_data) %>%
  filter(country %in% countries) %>%
  ggplot(aes(num_tracks %>% as.factor, avg_diff, fill = num_tracks)) +
  geom_errorbar(aes(ymin = diff_low, ymax = diff_high), width = 0.2, colour = "red") +
  geom_point(colour = "red") +
  scale_y_continuous(limits = c(0, 4)) +
  geom_col(aes(y = pred, alpha = 0.4)) +
  geom_errorbar(aes(ymin = pred_low, ymax = pred_high), width = 0.2) +
  facet_wrap(country ~ age_selection) +
  scale_fill_wsj()

@@

ready_data_two <-
  ready_data %>%
  group_by(country) %>%
  summarize(
    cum_diff = sum(difference, na.rm = TRUE),
    length = unique(length),
    num_tracks = unique(num_tracks),
    age_selection = unique(age_selection),
    central_examination = unique(central_examination),
    avg_track = unique(ztrack)
         )

# mod_tracking <-
#   ready_data_two %>%
#   lm(cum_diff ~ age_selection, data = .)

mod_tracking <-
  ready_data_two %>%
  filter(!is.na(age_selection)) %>%
  stan_glm(cum_diff ~ age_selection, data = .,
           family = "gaussian",
           prior = normal(0, 2),
           prior_intercept = normal(0, 5),
           prior_aux = cauchy(0, 1),
           refresh = -1)

ready_data_two %>%
  filter(!is.na(age_selection)) %>%
  mutate(pred_mean = posterior_predict(mod_tracking) %>% colMeans(),
         pred_median = posterior_predict(mod_tracking) %>% colMedians()) %>%
  select(country, cum_diff, pred_mean, pred_median) %>%
  gather(cat, value, -country) %>%
  ggplot(aes(country, value, fill = cat)) +
  geom_col(position = "dodge") +
  coord_flip()
